Hypothesis Testing

### 2019-09-24 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Creating R Markdown to show posterior visualizations for hypotheses stated in the paper.

---
title: "Results"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

# Load packages

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(bayesm)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)
```

# Causal pathway

Our theory and hypotheses are laid out in the causal pathway below. Organizational factors (**O**, or organizational practices like financial disclosure and accountability practices; **I**, or issue area; and **F**, or funding) all influence the decision to donate (**D**). Structural factors like an NGO's relationship with its host government (**G**) also influence donation behavior, but the relationship itself is shaped by both funding and issue area.

```{r causal-dag, fig.width=13/3, fig.height=2}
node_colors <- tribble(
  ~name, ~type,
  "D", "Outcome",
  "I", "Organizational factor",
  "F", "Organizational factor",
  "O", "Organizational factor",
  "G", "Structural factor"
)

# Set up DAG structure
theory_dag <- dagify(D ~ I + F + O + G,
                     G ~ I + F,
                     outcome = "D",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "dh", seed = 1234)

# Add node types/colors to DAG data
theory_dag$data <- theory_dag$data %>% 
  left_join(node_colors, by = "name")

# Make DAG plot
plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6, mapping = aes(color = type)) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  scale_adjusted() +
  theme_ngo() +
  theme(panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

# Show and save plot
plot_dag
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.pdf"),
       width = 13/3, height = 2, units = "in", device = cairo_pdf)
ggsave(plot_dag, filename = here("analysis", "output", "figures", "causal-path.png"),
       width = 13/3, height = 2, units = "in", type = "cairo", dpi = 300)
```

# Load data and model output

```{r load-data-output, warning=FALSE, message=FALSE}
intercept <- 0                           # Intercept-only
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept_noncentered.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit
```

# Model checking

```{r model-checking}
source(here::here("R", "stan_utility.R"))

# Thetas
draws_theta <- fit %>% 
  extract(
    pars = str_c("Theta[", 1:13, ",1]"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# Extract the L_Omega parameters only and look at trace plots, etc.

# L_Omega
draws_L_Omega <- fit %>% 
  extract(
    regex_pars = c("L_Omega"),
    inc_warmup = TRUE,
    permuted = FALSE
  )

draws_theta %>% 
  mcmc_hist_by_chain()

draws_theta %>% 
  mcmc_trace(
    n_warmup = 2000,
    facet_args = list(
      nrow = 4, 
      labeller = label_parsed
    )
  )

# # Check diagnostics
# check_all_diagnostics(fit)

# Check for divergences
check_div(fit)

# # Check the effective sample size (NOT WORKING?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (NOT WORKING?)
# check_rhat(fit)

# Check trace plots (SUBSET?)
color_scheme_set("mix-blue-red")
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    pars = str_c("Theta[", 1:13, ",1]"),
    n_warmup = 2000,
    facet_args = list(
      nrow = 2, 
      labeller = label_parsed
    )
  )

# ggsave(
#   "intercept_trace_noncentered.png",
#   path = here::here("analysis", "output", "figures"),
#   width = 12, height = 6, units = "in"
# )
```

# Extract draws

```{r extract-draws}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept_noncentered.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

# Plot marginals

```{r plot-marginals}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    # geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}

if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       # geom_halfeyeh(.width = .95) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

# # Save plot
# if (intercept == 1) file_name <- paste("intercept_marginal-posteriors.png")
# if (public_affairs == 1) file_name <- paste("public-affairs_marginal-posteriors.png")
# if (political_ideology == 1) file_name <- paste("political-ideology_marginal-posteriors.png")
# if (social_views == 1) file_name <- paste("social-views_marginal-posteriors.png")
# if (charity_voluntarism == 1) file_name <- paste("charity-voluntarism_marginal-posteriors.png")
# if (demographics == 1) file_name <- paste("demographics_marginal-posteriors.png")
# if (public_political == 1) file_name <- paste("public-political_marginal-posteriors.png")
# if (public_political_social == 1) file_name <- paste("public-political-social_marginal-posteriors.png")
# if (public_political_social_charity == 1) file_name <- paste("public-political-social-charity_marginal-posteriors.png")
# if (public_political_social_charity_demo == 1) file_name <- paste("public-political-social-charity-demos_marginal-posteriors.png")
# ggsave(
#   file_name,
#   path = here::here("analysis", "output", "figures"),
#   width = ifelse(intercept == 1, 12, 20), 
#   height = ifelse(sum(intercept, public_affairs, political_ideology, social_views, charity_voluntarism, demographics) == 1, 12, 20), 
#   units = "in"
# )
```

# Original computing environment

<button data-toggle="collapse" data-target="#sessioninfo" class="btn btn-primary btn-md btn-info">Here's what we used the last time we built this page</button>

<div id="sessioninfo" class="collapse">

```{r show-session-info, echo=TRUE, width=100}
writeLines(readLines(file.path(Sys.getenv("HOME"), ".R/Makevars")))

devtools::session_info()
```

</div>

>>>>

---
title: "Hypothesis Testing"
output: github_document
---

The purpose of this R Markdown is to visualize the results to the hypotheses proposed at the beginning of the paper.

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(bayesm)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)
```

Run this code below to specify the covariate.
```{r plot-marginals}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

```

#### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?

```{r}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

```

#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?

```{r}

```

# Hypotheses:
# We theorize that structural characteristics like an NGO’s host-country political and legal environment can serve as heuristics and shortcuts for donors.
# Donors who see that an NGO faces general legal trouble abroad will use that knowledge to decide whether or not to donate.
# We also theorize that non-structural organizational characteristics like managerial practices, funding sources, and issue area also serve as heuristics and influence donation patterns.
# In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.
